Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-07-16 draft.tex
update references to JLEO style guide

\item \hangindent=1cm Acemoglu, Daron, Golosov, Mikhail, Tsyvinski, Aleh, and Pierre Yared. 2012. "A Dynamic Theory of Resource Wars." 
\emph{The Quarterly Journal of Economics} 127: 283-331.

\item \hangindent=1cm Bahcheli, Tozun, Barry Martmann, and Henry Srebrnik, eds. 2004 "De Facto States: The Quest for Sovereignty." New York, NY: Routledge.

\item \hangindent=1cm Bakke, Kristin M. 2011 "After the war ends: violence and vialibity of post-Soviet unrecognized states." in: Caspersen, Nina, and Gareth Stansfield. \emph{Unrecognized States in the International System}. New York, NY: Routledge.

\item \hangindent=1cm Bakke, Kristin M., John O'Loughlin, Gerard Toal, and Michael D. Ward.  2013.  "Convincing State-Builders? Disaggregating Internal Legitimacy in Abkhazia."  \emph{International Studies Quarterly.}

@@

\item \hangindent=1cm Balch-Lindsay, Dylan, Andrew J. Enterline, and Kyle A. Joyce.  2008.  "Third-Party Intervention and the Civil War Process."  \emph{Journal of Peace Research} 45: 345-63.

\item \hangindent=1cm Baliga, Sandeep, and Tomas Sjostrom. 2012. "The Strategy of Manipulating Conflict." \emph{The American Economic Review} 102 (6): 2897-2922.

\item \hangindent=1cm Bevi\'{a}, Carmen and Luis C. Corch\'{o}n. 2010. ``Peace Agreements without Commitment.'' \emph{Games and Economic Behavior} 68 (2): 469-487.

\item \hangindent=1cm Bueno de Mesquita, Ethan. 2013. ``Rebel tactics.'' \emph{Journal of Political Economy} 121 (2): 323-357.

\item \hangindent=1cm Caspersen, Nina. 2013. "Unrecognized States: The Struggle for Sovereignty in the Modern International System." Malden, MA: Polity Press.

\item \hangindent=1cm Caspersen, Nina, and Gareth Stansfield. 2011. "Unrecognized States in the International System." New York, NY: Routledge.

@@

\item \hangindent=1cm Coggins, Bridget. 2011. "Friends in High Places: International Politics and the Emergence of States from Secessionism." \emph {International Organization} 65 (03): 433-467.

@@

\item \hangindent=1cm Crawford, James. 2006. "The Creation of States in International Law." Oxford: Oxford University Press.

@@

\item \hangindent=1cm Doyle, Michael W., and Nicholas Sambanis. 2006. "Making War and Building Peace: United Nations Peace Operations." Princeton: Princeton University Press.

\item \hangindent=1cm Elbadawi, Ibrahim, and Nicholas Sambanis. 2000. "External Interventions and the Duration of Civil Wars." 2433.

@@

\item \hangindent=1cm Fearon, James D.  1994.  "Domestic Political Audiences and the Escalation of International Disputes."  \emph{The American Political Science Review} 88: 577-92.

\item \hangindent=1cm Fearon, James D., and David D. Laitin. 2003. "Ethnicity, Insurgency, and Civil War." \emph {American Political Science Review} 97 (01): 75-90.

\item \hangindent=1cm Fearon, James D. 2004. "Why Do Some Civil Wars Last So Much Longer than Others?" \emph {Journal of Peace Research} 41 (3): 275-301.

\item \hangindent=1cm Geldenhuys, Deon. 2009. "Contested States in World Politics." Basingstoke: Palgrave McMillan.

@@

\item \hangindent=1cm Grossman, Herschel I. 2004. ''Peace and war in territorial disputes.'' No. w10601. National Bureau of Economic Research.

\item \hangindent=1cm Hirshleifer, Jack, Boldrin, Michele, and David K Levine. 2009. ''The slippery slope of concession.'' \emph{Economic Inquiry} 47 (2): 197-205.

\item \hangindent=1cm Jackson, Matthew O., and Massimo Morelli. 2007. "Political bias and war." \emph{The American Economic Review} 97 (4): 1353-1373.

\item \hangindent=1cm King, Charles. 2001. "The Benefits of Ethnic War: Understanding Eurasia's Unrecognized States." \emph{World Politics} 53 (4): 524-552.

\item \hangindent=1cm Kingston, Paul, and Ian S. Spears, eds. 2004. "States-Within-States." New York, NY: Palgrave McMillan.

\item \hangindent=1cm Kolst\o, P{\aa}l. 2006. "The Sustainability and Future of Unrecognized Quasi-States." \emph {Journal of Peace Research} 43 (6): 723-740.

\item \hangindent=1cm Licklider, Roy. 1995. "The Consequences of Negotiated Settlements in Civil Wars, 1945-1993." \emph {American Political Science Review} (89): 681-90.

@@

\item \hangindent=1cm Lynch, Dov. 2004. "Engaging Eurasia's Separatist States." Washington, DC: U.S. Institute of Peace.

\item \hangindent=1cm Mailath, George J., and Larry Samuelson. 2006. "Repeated Games and Reputation." New York, NY: Oxford University Press.

\item \hangindent=1cm McBride, Michael, and Stergios Skaperdas. 2014. "Conflict, settlement, and the shadow of the future." \emph{Journal of Economic Behavior $\&$ Organization} 105: 75-89.

\item \hangindent=1cm Owtram, Francis. 2011. "The foreign policies of unrecognized states." in: Caspersen, Nina, and Gareth Stansfield. \emph{Unrecognized States in the International System}. New York, NY: Routledge.

\item \hangindent=1cm Pegg, Scott. 1998. "International society and the de facto state." New York: Ashgate.

@@

\item \hangindent=1cm Regan, P.M. 2002. "Civil wars and foreign powers: Outside intervention in intrastate conflict." Ann Arbor: University of Michigan Press.

\item \hangindent=1cm Roeder, Philip G. 2007. "Where nation-states come from: institutional change in the age of nationalism." Princeton: Princeton University Press.

\item \hangindent=1cm Salehyan, Idean, Kristian Skrede Gleditsch, and David E. Cunningham. 2011. "Explaining External Support for Insurgent Groups." \emph {International Organization} 65 (04): 709-744.

\item \hangindent=1cm Schwarz, Michael, and Konstantin Sonin. 2008. "A theory of brinkmanship, conflicts, and commitments." \emph{Journal of Law, Economics, and Organization} 24 (1): 163-183.

\item \hangindent=1cm Schultz, Kenneth A. 2010. "The Enforcement Problem in Coercive Bargaining: Interstate Conflict over Rebel Support in Civil Wars." \emph {International Organization} 64 (02): 281-312.

@@

\item \hangindent=1cm Stanislawski, Bartosz H. 2008. "Para-States, Quasi-States, and Black Spots: Perhaps Not States, But Not `Ungoverned Territories,' Either." \emph {International Studies Review} 10 (2): 366-396.

@@

\item \hangindent=1cm van Houten, Pieter. 1998. "The role of a minority's reference state in ethnic relations." \emph {European Journal of Sociology / Archives Europennes de Sociologie} 39 (01): 110-146.

\item \hangindent=1cm Walter, Barbara F. 1997. "The Critical Barrier to Civil War Settlement." \emph {International Organization} 51 (03): 335-364.

\item \hangindent=1cm Walter, Barbara F.. 2002. "Committing to Peace: The successful settlement of civil wars." Princeton: Princeton University Press.

@@

\item \hangindent=1cm Yared, Pierre. 2010. ``A Dynamic Theory of War and Peace.'' \emph{Journal of Economic Theory} 145: 1921-1950.

\item \hangindent=1cm Zacher, Mark W. 2001. "The Territorial Integrity Norm: International Boundaries and the Use of Force." \emph {International Organization} 55 (02): 215-250.

>>>>

\item \hangindent=1cm Acemoglu, Daron, Mikhail Golosov, Aleh Tsyvinski, and Pierre Yared. 2012. "A Dynamic Theory of Resource Wars," 
127 \emph{The Quarterly Journal of Economics} 283-331.

\item \hangindent=1cm Bahcheli, Tozun, Barry Martmann, and Henry Srebrnik. 2004. \emph{De Facto States: The Quest for Sovereignty.} New York, NY: Routledge.

\item \hangindent=1cm Bakke, Kristin M. 2011 "After the War Ends: Violence and Vialibity of Post-Soviet Unrecognized States," in Nina Caspersen and Gareth Stansfield, eds., \emph{Unrecognized States in the International System}. New York, NY: Routledge.

\item \hangindent=1cm Bakke, Kristin M., John O'Loughlin, Gerard Toal, and Michael D. Ward. 2013. "Convincing State-Builders? Disaggregating Internal Legitimacy in Abkhazia," 58 \emph{International Studies Quarterly} 591-607.

@@

\item \hangindent=1cm Balch-Lindsay, Dylan, Andrew J. Enterline, and Kyle A. Joyce. 2008. "Third-Party Intervention and the Civil War Process," 45 \emph{Journal of Peace Research} 345-63.

\item \hangindent=1cm Baliga, Sandeep, and Tomas Sjostrom. 2012. "The Strategy of Manipulating Conflict," 102 \emph{The American Economic Review} 2897-2922.

\item \hangindent=1cm Bevi\'{a}, Carmen and Luis C. Corch\'{o}n. 2010. ``Peace Agreements without Commitment,'' 68 \emph{Games and Economic Behavior} 469-87.

\item \hangindent=1cm Bueno de Mesquita, Ethan. 2013. ``Rebel tactics,'' 121 \emph{Journal of Political Economy} 323-57.

\item \hangindent=1cm Caspersen, Nina. 2013. \emph{Unrecognized States: The Struggle for Sovereignty in the Modern International System.} Malden, MA: Polity Press.

\item \hangindent=1cm Caspersen, Nina, and Gareth Stansfield. 2011. \emph{Unrecognized States in the International System.} New York, NY: Routledge.

@@

\item \hangindent=1cm Coggins, Bridget. 2011. "Friends in High Places: International Politics and the Emergence of States from Secessionism," 65 \emph {International Organization} 433-67.

@@

\item \hangindent=1cm Crawford, James. 2006. \emph{The Creation of States in International Law.} Oxford: Oxford University Press.

@@

\item \hangindent=1cm Doyle, Michael W., and Nicholas Sambanis. 2006. \emph{Making War and Building Peace: United Nations Peace Operations.} Princeton, NJ: Princeton University Press.

\item \hangindent=1cm Elbadawi, Ibrahim, and Nicholas Sambanis. 2000. "External Interventions and the Duration of Civil Wars." World Bank Policy Research Working Paper 2433.

@@

\item \hangindent=1cm Fearon, James D. 1994. "Domestic Political Audiences and the Escalation of International Disputes," 88 \emph{The American Political Science Review} 577-92.

\item \hangindent=1cm Fearon, James D., and David D. Laitin. 2003. "Ethnicity, Insurgency, and Civil War," 97 \emph {American Political Science Review} 75-90.

\item \hangindent=1cm Fearon, James D. 2004. "Why Do Some Civil Wars Last So Much Longer than Others?" 41 \emph {Journal of Peace Research} 275-301.

\item \hangindent=1cm Geldenhuys, Deon. 2009. \emph{Contested States in World Politics.} Basingstoke: Palgrave McMillan.

@@

\item \hangindent=1cm Grossman, Herschel I. 2004. ''Peace and war in territorial disputes.'' No. w10601. National Bureau of Economic Research. Working Paper

\item \hangindent=1cm Hirshleifer, Jack, Michele Boldrin, and David K Levine. 2009. ''The slippery slope of concession,'' 47 \emph{Economic Inquiry} 197-205.

\item \hangindent=1cm Jackson, Matthew O., and Massimo Morelli. 2007. "Political bias and war," 97 \emph{The American Economic Review} 1353-73.

\item \hangindent=1cm King, Charles. 2001. "The Benefits of Ethnic War: Understanding Eurasia's Unrecognized States," 53 \emph{World Politics} 524-552.

\item \hangindent=1cm Kingston, Paul, and Ian S. Spears. 2004. \emph{States-Within-States.} New York, NY: Palgrave McMillan.

\item \hangindent=1cm Kolst\o, P{\aa}l. 2006. "The Sustainability and Future of Unrecognized Quasi-States," 43 \emph {Journal of Peace Research} 723-40.

\item \hangindent=1cm Licklider, Roy. 1995. "The Consequences of Negotiated Settlements in Civil Wars, 1945-1993," 89 \emph {American Political Science Review} 681-90.

@@

\item \hangindent=1cm Lynch, Dov. 2004. \emph{Engaging Eurasia's Separatist States.} Washington, DC: U.S. Institute of Peace.

\item \hangindent=1cm Mailath, George J., and Larry Samuelson. 2006. \emph{Repeated Games and Reputation.} New York, NY: Oxford University Press.

\item \hangindent=1cm McBride, Michael, and Stergios Skaperdas. 2014. "Conflict, Settlement, and the Shadow of the Future," 105 \emph{Journal of Economic Behavior $\&$ Organization} 75-89.

\item \hangindent=1cm Owtram, Francis. 2011. "The Foreign Policies of Unrecognized States," in: Nina Caspersen and Gareth Stansfield, eds., \emph{Unrecognized States in the International System}. New York, NY: Routledge.

\item \hangindent=1cm Pegg, Scott. 1998. \emph{International Society and the de Facto State.} New York, NY: Ashgate.

@@

\item \hangindent=1cm Regan, P.M. 2002. \emph{Civil Wars and Foreign Powers: Outside Intervention in Intrastate Conflict.} Ann Arbor, MI: University of Michigan Press.

\item \hangindent=1cm Roeder, Philip G. 2007. \emph{Where Nation-states Come From: Institutional Change in the Age of Nationalism.} Princeton, NJ: Princeton University Press.

\item \hangindent=1cm Salehyan, Idean, Kristian Skrede Gleditsch, and David E. Cunningham. 2011. "Explaining External Support for Insurgent Groups," 65 \emph {International Organization} 709-44.

\item \hangindent=1cm Schwarz, Michael, and Konstantin Sonin. 2008. "A Theory of Brinkmanship, Conflicts, and Commitments." 24 \emph{Journal of Law, Economics, and Organization} 163-183.

\item \hangindent=1cm Schultz, Kenneth A. 2010. "The Enforcement Problem in Coercive Bargaining: Interstate Conflict over Rebel Support in Civil Wars," 64 \emph{International Organization} 281-312.

@@

\item \hangindent=1cm Stanislawski, Bartosz H. 2008. "Para-States, Quasi-States, and Black Spots: Perhaps Not States, But Not `Ungoverned Territories,' Either," 10 \emph{International Studies Review} 366-396.

@@

\item \hangindent=1cm van Houten, Pieter. 1998. "The Role of a Minority's Reference State in Ethnic Relations." 39 \emph {European Journal of Sociology / Archives Europennes de Sociologie} 110-146.

\item \hangindent=1cm Walter, Barbara F. 1997. "The Critical Barrier to Civil War Settlement," 51 \emph {International Organization} 335-64.

\item \hangindent=1cm ----. 2002. \emph{Committing to Peace: The Successful Settlement of Civil Wars.} Princeton, NJ: Princeton University Press.

@@

\item \hangindent=1cm Yared, Pierre. 2010. ``A Dynamic Theory of War and Peace,'' 145 \emph{Journal of Economic Theory} 1921-50.

\item \hangindent=1cm Zacher, Mark W. 2001. "The Territorial Integrity Norm: International Boundaries and the Use of Force," 55 \emph {International Organization} 215-50.
